Journal and article coverage

### 2025-02-18 analysis/manuscript.qmd
Continue coverage analysis

This study aims to demonstrate the suitability of open scholarly data sources for assessing the impact of transformative agreements on hybrid open access.
As shown in Figure \ref{fig:workflow}, the methodology involved comparing hoaddata, an openly available collection of open research information on hybrid open access, with the bibliometric databases Web of Science and Scopus.
The subsequent section, introduces the initial data sources followed by a presentation of the necessary pre-processing steps to obtain eligible articles from transformative agreements by using author roles (first and corresponding) and harmonised affiliation data.
<!-- Overall, xxxx hybrid journals from xxx agreements that published at least one open access article between 2019 and 2023. formed the basis of this study. -->

@@

hoaddata, developed and maintained by the author to support open access monitoring and research [@Jahn_2025], is an R data package comprising information about the uptake of hybrid open access since 2017 from several openly available data sources.
It combines article-level metadata from Crossref and OpenAlex with transformative agreement information from the cOAlition S Journal Checker Tool (JCT), which links journal and institutional data to agreements in the ESAC registry.

More specifically, hoaddata uses a unified dataset of historic JCT snapshots since July 2021, which were enriched ISSN variants linked to an ISSN-L and associated ROR-IDs representing university hospitals or institutes of large research organisations, according to OpenAlex' institution entity.
A comprehensive exclusion of fully open access journals using  multiple journal lists (DOAJ, OpenAlex, Bielefeld)  was performed to identify hybrid journals, as described in @Jahn_2025.
hoaddata relies on Crossref for obtaining journal publication volume and open access status through Creative Commons licence information relative to the published version ("version of record").
Because of limited affiliation metadata in Crossref [@van_Eck_2022], hoaddata sources first-author affiliations from OpenAlex.

@@

<!-- The JCT journal data was enriched with the linking ISSN (ISSN-L) according to the ISSN Registry Agency.
A comprehensive exclusion of fully open access journals was performed, following the methodology described in @jahn_2025.
This involved checking multiple journal lists (DOAJ, OpenAlex, Bielefeld) and article-level investigations.
The JCT institution data was enriched with ROR-IDs from associated institutions, such as university hospitals or institutes of large research organisations such as the Max Planck Society, according to OpenAlex' institution entity.
<!-- In total, xxxx hybrid journals could be linked to xxx agreements listed in the ESAC Transformative Agreements Registry, which formed to basis for obtaining article-level data including author affiliations, open access status ans document types. -->
Article metadata was retrieved from each databse using all ISSN variants linked to an ISSN-L. The metadata included DOIs, publication dates, article types, open access information as well as author roles and institutional affiliations.

The publication year for each article was determined using the earliest known publication date. 
For articles in hoaddata, this corresponded to Crossref's issued date.

Publication years were determined using the earliest known date of publication in a journal.
In the case of Crossref, the article data source for hoaddata, this was the issued date<!--, although variations were observed (check ref)-->.
For Web of Science and Scopus, the earliest publication date was used where available, with Scopus dates specifically determined by the KB through version tracking of the raw data.

@@

As a result of the comprehensive data processing described above, datasets on open access in hybrid journals included in transformative agreements were produced for each database at country and journal level by year.
@tbl-methods_overview_tab provides a general overview of the coverage between 2019 and 2023 per database.
It shows that the majority of hybrid journals published at least one original article or review marked as core during the five-year period.
These journals formed the basis for the subsequent aggregation of publication metrics.

@@

While hoaddata only covers articles with a DOI, the Scopus and Web of Science figures were also aggregated using the database identifier.
A subsequent comparison of DOI coverage shows that non-core articles in Web of Science often lacked a DOI.
This was particularly the case for meeting abstracts, a particular feature of this database.
Open access indicators were aggregated by DOI, as Unpaywall only collects information on open access status for articles with a DOI.
A closer look at the core articles with affiliation data reveals a lack of data on corresponding authors in the case of OpenAlex, the affiliation data source used by hoaddata, compared to Web of Science and Scopus.
Only about two-thirds of the articles examined provided corresponding author affiliations.
For first authors, the proportion was `r methods_overview_table_df |> filter(indicator == "First author articles") |> pull(hoad) / methods_overview_table_df |> filter(indicator == "Core articles with DOI") |> pull(hoad) * 100`%.
Accordingly, only first author data for hoaddata are considered in the following analysis.

@@

>>>>

This study aims to demonstrate the suitability of open scholarly data sources for assessing the impact of transformative agreements on hybrid open access.
As shown in Figure \ref{fig:workflow}, the methodology involved comparing hoaddata, an openly available collection of open research information on hybrid open access, with the bibliometric databases Web of Science and Scopus.
This section introduces the initial data sources followed by a presentation of the necessary pre-processing steps to obtain eligible articles from transformative agreements by using author roles (first and corresponding) and harmonised affiliation data.
<!-- Overall, xxxx hybrid journals from xxx agreements that published at least one open access article between 2019 and 2023. formed the basis of this study. -->

@@

hoaddata, developed and maintained by the author to support open access monitoring and research [@Jahn_2025], is an R data package comprising information about the uptake of hybrid open access since 2017 collected from several openly available data sources.
It combines article-level metadata from Crossref and OpenAlex with transformative agreement information from the cOAlition S Journal Checker Tool (JCT), which links journal and institutional data to agreements in the ESAC registry.

As discussed elsewhere [@Jahn_2025], hoaddata uses a unified dataset of historic JCT snapshots since July 2021, which were enriched with ISSN variants linked to an ISSN-L and associated ROR-IDs representing university hospitals or institutes of large research organisations, according to OpenAlex' institution entity.
A comprehensive exclusion of fully open access journals using  multiple journal lists (DOAJ, OpenAlex, Bielefeld)  was performed to identify hybrid journals.
hoaddata relies on Crossref for obtaining journal publication volume and open access status through Creative Commons licence information relative to the published version ("version of record").
Because of limited affiliation metadata in Crossref [@van_Eck_2022], hoaddata sources first-author affiliations from OpenAlex.

@@

<!-- The JCT journal data was enriched with the linking ISSN (ISSN-L) according to the ISSN Registry Agency.
A comprehensive exclusion of fully open access journals was performed, following the methodology described in @jahn_2025.
This involved checking multiple journal lists (DOAJ, OpenAlex, Bielefeld) and article-level investigations.
The JCT institution data was enriched with ROR-IDs from associated institutions, such as university hospitals or institutes of large research organisations such as the Max Planck Society, according to OpenAlex' institution entity.
<!-- In total, xxxx hybrid journals could be linked to xxx agreements listed in the ESAC Transformative Agreements Registry, which formed to basis for obtaining article-level data including author affiliations, open access status ans document types. -->
Article metadata was retrieved from each databse using all ISSN variants linked to an ISSN-L. The metadata included DOIs, publication dates, article types, open access information as well as author roles and institutional affiliations.
Publication years were determined using the earliest known date of publication in a journal.
articles in hoaddata, this corresponded to Crossref's issued date.<!--, although variations were observed (check ref)-->
For Web of Science and Scopus, the earliest publication date was used where available, with Scopus dates specifically determined by the KB through version tracking of the raw data.

@@

As a result of the comprehensive data processing described above, datasets on open access in hybrid journals included in transformative agreements were aggregated for each database at country and journal level by year.
@tbl-methods_overview_tab provides a general overview of the coverage between 2019 and 2023 per database.
It shows that the majority of hybrid journals published at least one original research article or review marked as core during the five-year period.
These journals formed the basis for the subsequent aggregation of publication metrics.

@@

While hoaddata only covers articles with a DOI, Scopus and Web of Science publication metrics were aggregated using the database identifier.
A subsequent comparison of DOI coverage shows that non-core articles in Web of Science often lacked a DOI.
This was particularly the case for meeting abstracts, which are notably prevalent in Health Sciences journals [@Melero_Fuentes_2025].
Open access indicators were aggregated by DOI, as Unpaywall only collects information on open access status for articles with a DOI.
A closer look at the core articles with affiliation data reveals a lack of data on corresponding authors in the case of OpenAlex, the affiliation data source used by hoaddata, compared to Web of Science and Scopus.
Only about two-thirds of the articles examined provided corresponding author affiliations.
For first authors, the proportion was `r methods_overview_table_df |> filter(indicator == "First author articles") |> pull(hoad) / methods_overview_table_df |> filter(indicator == "Core articles with DOI") |> pull(hoad) * 100`%.
Therefore, only first author data for hoaddata were considered in the following analysis.

@@

First, I will present a coverage analysis. 
Then, I investigate hybrid open access uptake using the same methods for each database and the compare results against each other in order to assess the suitablility of the biblioemtric databases to examine transofrmative agreements.

## Coverage comparision

```{r}
jn_upset_articles <- readr::read_csv(here::here("data", "jn_upset_articles.csv"))

all_jns <- jn_upset_articles |> 
  distinct(issn_l)

union_jns <- jn_upset_articles |>
  filter(WoS == TRUE, Crossref == TRUE, Scopus == TRUE) |>
  distinct(issn_l)

upset_data <- jn_upset_articles |> 
   mutate(overlap = case_when(Crossref == TRUE & WoS == TRUE & Scopus == TRUE ~ doi_in_wos_or_scopus,
                             Crossref == TRUE & WoS == FALSE & Scopus == TRUE ~ doi_in_scopus,
                             Crossref == TRUE & WoS == TRUE & Scopus == FALSE ~ doi_in_wos,
                             Crossref == TRUE & WoS == FALSE & Scopus == FALSE ~ n_cr,
                             Crossref == FALSE & WoS == FALSE & Scopus == TRUE ~ doi_in_scopus,
                             Crossref == FALSE & WoS == TRUE & Scopus == FALSE ~ doi_in_wos,
                             Crossref == FALSE & WoS == TRUE & Scopus == TRUE ~ doi_in_wos_or_scopus))

```

Figure \ref{fig-upset_coverage_results} presents the coverage of hybrid journals included in transformative agreements, visualising the intersections of journals and articles across the examined databases as an UpSet graph [@Lex_2014; @ComplexUpset].
The analysis included hybrid journals that published at least one open access article between 2019 and 2023, based on open access status information from each database.
Only original research articles and reviews were considered in the analysis.

```{r upset_coverage_results, fig.asp=0.75}
#| fig-cap: "Upset graph"
#| label: fig-upset_coverage_results
# Helper function to make text labels the same size as axis labels as seen in
# <https://wjschne.github.io/posts/making-text-labels-the-same-size-as-axis-labels-in-ggplot2/>
# Todo: Learn how to invoke it

ggtext_size <- function(base_size, ratio = 0.8) {
  ratio * base_size / ggplot2::.pt
}

bar_width <- 0.7
size <- get_size_mode("exclusive_intersection")

upset_overview <- ComplexUpset::upset(
  upset_data,
  c("Crossref", "WoS", "Scopus"),
  # Only journals in Crossref
  min_size = 30,
  set_sizes = FALSE,
  stripes = "transparent",
  # wrap = TRUE,
  name = "Data Source Coverage",
  base_annotations = list(
    "Journals" = (
      ComplexUpset::intersection_size(
        counts = FALSE,
        text = list(size = 8 / .pt),
        text_mapping = aes(
          label = paste0(!!upset_text_percentage(), '\n(', format(!!size, big.mark = ","), ')'),
          colour = ifelse(!!size > 5000, 'on_bar', 'on_background'),
          y = ifelse(!!size > 5000, !!size - 4000, !!size)
        ), width = bar_width
      ) +
        scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
        ggtitle("A")
    )
  ),
  annotations = list(
    "Journal size\n(log scale)" = (
      ggplot(mapping = aes(x = intersection, y = n)) +
        geom_boxplot(outliers = FALSE, width = bar_width) +
        scale_y_log10(labels =  scales::number_format(big.mark = ",")) +
        ggtitle("C")
    ),
    "Articles" = (
      ggplot(mapping = aes(y = n_cr)) +
        geom_bar(
          stat = "identity",
          color = "grey80",
          width = bar_width,
          aes(fill = "All")
        ) +
        geom_bar(
          aes(y = overlap, fill = "Shared"),
          stat = "identity",
          width = bar_width,
          color = "#0091c8"
        ) +
        scale_fill_manual(
          values = c(
            `All` = "grey80",
            `Shared` = "#0091c8"
          ),
          name = "DOI"
        ) +
        scale_y_continuous(labels =  scales::number_format(big.mark = ","),
                           breaks = c(0, 2500000, 5000000, 7500000)) +
        ggtitle("B")
    )
  ),
  matrix = (intersection_matrix(geom = geom_point(
    shape = "square", size = 2
  )))
)
upset_overview & my_upset_theme
```
Journal coverage analysis revealed that `r round(nrow(union_jns) / nrow(all_jns) * 100)`% (n = `r nrow(union_jns)`) of hybrid journals included in transformative agreements were indexed in all three databases ( \ref{fig-upset_coverage_results}A).
The second-largest set consisted of journals indexed in both hoaddata and Scopus, comprising `r round( jn_upset_articles |> filter(WoS == FALSE, Crossref == TRUE, Scopus == TRUE) |> distinct(issn_l) |> nrow() / nrow(all_jns) * 100)`% (n = `r jn_upset_articles |> filter(WoS == FALSE, Crossref == TRUE, Scopus == TRUE) |>  nrow()`) of hybrid journals.
Notably, `r round(jn_upset_articles |> filter(WoS == FALSE, Crossref == TRUE, Scopus == FALSE) |> distinct(issn_l) |> nrow() / nrow(all_jns) * 100)`% (n = `r jn_upset_articles |> filter(WoS == FALSE, Crossref == TRUE, Scopus == FALSE) |>  nrow()`) of journals were exclusively contained in hoaadata, while `r round( jn_upset_articles |> filter(WoS == TRUE, Crossref == FALSE, Scopus == TRUE) |> distinct(issn_l) |> nrow() / nrow(all_jns) * 100)`% (n = `r jn_upset_articles |> filter(WoS == TRUE, Crossref == FALSE, Scopus == TRUE) |>  nrow()`) were only found in the proprietory databases Scopus and Web of Science.
Upon insepction, this latter group mainly represents hybrid journals for which no open access evidence could be retrieved from Crossref, which serves as the open access evidence source for hoaddata.

In terms of article coverage, Fig B shows the DOI overlap, distinguihsing between a shared corpus and just those where a DOI was only available through hoaddata.
Upon inspection, reasons for lackign DOI coverage in proprietory database were different publication dates and differenc ein document type definitions. 
As such, demosntrates certain uncertainies using the open approach.
Overall, The majority of articles can be found

Using DOIs also the size of journals were calculated (Fig C). It highlights thate large spread in the intersection between all three datasett. Journals are, on average, smaller than those just covered by one or two sources.In particular journals exlcusively covered by hoaddata are significant smaller than those covered by all three sources.

This study compares results drawn from the openly available and regularly updated hoaddata, an R package leveraging the open scholarly data sources Crossref and OpenAlex, with the in-house database of the German Competence Network 
Overall, xxxx hybrid journals included in xxx agreements that published at least one open access article between 2019 and 2023.

### 2025-02-18 analysis/manuscript.tex
Continue coverage analysis

This study aims to demonstrate the suitability of open scholarly data
sources for assessing the impact of transformative agreements on hybrid
open access. As shown in Figure \ref{fig:workflow}, the methodology
involved comparing hoaddata, an openly available collection of open
research information on hybrid open access, with the bibliometric
databases Web of Science and Scopus. The subsequent section, introduces
the initial data sources followed by a presentation of the necessary
pre-processing steps to obtain eligible articles from transformative
agreements by using author roles (first and corresponding) and
harmonised affiliation data.

@@

hoaddata, developed and maintained by the author to support open access
monitoring and research (Jahn, 2025), is an R data package comprising
information about the uptake of hybrid open access since 2017 from
several openly available data sources. It combines article-level
metadata from Crossref and OpenAlex with transformative agreement
information from the cOAlition S Journal Checker Tool (JCT), which links
journal and institutional data to agreements in the ESAC registry.

More specifically, hoaddata uses a unified dataset of historic JCT
snapshots since July 2021, which were enriched ISSN variants linked to
an ISSN-L and associated ROR-IDs representing university hospitals or
institutes of large research organisations, according to OpenAlex'
institution entity. A comprehensive exclusion of fully open access
journals using multiple journal lists (DOAJ, OpenAlex, Bielefeld) was
performed to identify hybrid journals, as described in Jahn (2025).
hoaddata relies on Crossref for obtaining journal publication volume and
open access status through Creative Commons licence information relative
to the published version (``version of record''). Because of limited
affiliation metadata in Crossref (Eck \& Waltman, 2022), hoaddata
sources first-author affiliations from OpenAlex.

@@

Article metadata was retrieved from each databse using all ISSN variants
linked to an ISSN-L. The metadata included DOIs, publication dates,
article types, open access information as well as author roles and
institutional affiliations.

The publication year for each article was determined using the earliest
known publication date. For articles in hoaddata, this corresponded to
Crossref's issued date.

Publication years were determined using the earliest known date of
publication in a journal. In the case of Crossref, the article data
source for hoaddata, this was the issued date. For Web of Science and
Scopus, the earliest publication date was used where available, with
Scopus dates specifically determined by the KB through version tracking
of the raw data.

@@

As a result of the comprehensive data processing described above,
datasets on open access in hybrid journals included in transformative
agreements were produced for each database at country and journal level
by year. Table~\ref{tbl-methods_overview_tab} provides a general
overview of the coverage between 2019 and 2023 per database. It shows
that the majority of hybrid journals published at least one original
article or review marked as core during the five-year period. These
journals formed the basis for the subsequent aggregation of publication
metrics.

@@

While hoaddata only covers articles with a DOI, the Scopus and Web of
Science figures were also aggregated using the database identifier. A
subsequent comparison of DOI coverage shows that non-core articles in
Web of Science often lacked a DOI. This was particularly the case for
meeting abstracts, a particular feature of this database. Open access
indicators were aggregated by DOI, as Unpaywall only collects
information on open access status for articles with a DOI. A closer look
at the core articles with affiliation data reveals a lack of data on
corresponding authors in the case of OpenAlex, the affiliation data
source used by hoaddata, compared to Web of Science and Scopus. Only
about two-thirds of the articles examined provided corresponding author
affiliations. For first authors, the proportion was 89\%. Accordingly,
only first author data for hoaddata are considered in the following
analysis.

@@

@@

@@

>>>>

This study aims to demonstrate the suitability of open scholarly data
sources for assessing the impact of transformative agreements on hybrid
open access. As shown in Figure \ref{fig:workflow}, the methodology
involved comparing hoaddata, an openly available collection of open
research information on hybrid open access, with the bibliometric
databases Web of Science and Scopus. This section introduces the initial
data sources followed by a presentation of the necessary pre-processing
steps to obtain eligible articles from transformative agreements by
using author roles (first and corresponding) and harmonised affiliation
data.

@@

hoaddata, developed and maintained by the author to support open access
monitoring and research (Jahn, 2025), is an R data package comprising
information about the uptake of hybrid open access since 2017 collected
from several openly available data sources. It combines article-level
metadata from Crossref and OpenAlex with transformative agreement
information from the cOAlition S Journal Checker Tool (JCT), which links
journal and institutional data to agreements in the ESAC registry.

As discussed elsewhere (Jahn, 2025), hoaddata uses a unified dataset of
historic JCT snapshots since July 2021, which were enriched with ISSN
variants linked to an ISSN-L and associated ROR-IDs representing
university hospitals or institutes of large research organisations,
according to OpenAlex' institution entity. A comprehensive exclusion of
fully open access journals using multiple journal lists (DOAJ, OpenAlex,
Bielefeld) was performed to identify hybrid journals. hoaddata relies on
Crossref for obtaining journal publication volume and open access status
through Creative Commons licence information relative to the published
version (``version of record''). Because of limited affiliation metadata
in Crossref (Eck \& Waltman, 2022), hoaddata sources first-author
affiliations from OpenAlex.

@@

Article metadata was retrieved from each databse using all ISSN variants
linked to an ISSN-L. The metadata included DOIs, publication dates,
article types, open access information as well as author roles and
institutional affiliations. Publication years were determined using the
earliest known date of publication in a journal. articles in hoaddata,
this corresponded to Crossref's issued date. For Web of Science and
Scopus, the earliest publication date was used where available, with
Scopus dates specifically determined by the KB through version tracking
of the raw data.

@@

As a result of the comprehensive data processing described above,
datasets on open access in hybrid journals included in transformative
agreements were aggregated for each database at country and journal
level by year. Table~\ref{tbl-methods_overview_tab} provides a general
overview of the coverage between 2019 and 2023 per database. It shows
that the majority of hybrid journals published at least one original
research article or review marked as core during the five-year period.
These journals formed the basis for the subsequent aggregation of
publication metrics.

@@

While hoaddata only covers articles with a DOI, Scopus and Web of
Science publication metrics were aggregated using the database
identifier. A subsequent comparison of DOI coverage shows that non-core
articles in Web of Science often lacked a DOI. This was particularly the
case for meeting abstracts, which are notably prevalent in Health
Sciences journals (Melero-Fuentes et al., 2025). Open access indicators
were aggregated by DOI, as Unpaywall only collects information on open
access status for articles with a DOI. A closer look at the core
articles with affiliation data reveals a lack of data on corresponding
authors in the case of OpenAlex, the affiliation data source used by
hoaddata, compared to Web of Science and Scopus. Only about two-thirds
of the articles examined provided corresponding author affiliations. For
first authors, the proportion was 89\%. Therefore, only first author
data for hoaddata were considered in the following analysis.

@@

First, I will present a coverage analysis. Then, I investigate hybrid
open access uptake using the same methods for each database and the
compare results against each other in order to assess the suitablility
of the biblioemtric databases to examine transofrmative agreements.

\subsection{Coverage comparision}\label{coverage-comparision}

Figure \ref{fig-upset_coverage_results} presents the coverage of hybrid
journals included in transformative agreements, visualising the
intersections of journals and articles across the examined databases as
an UpSet graph (Krassowski, 2020; Lex et al., 2014). The analysis
included hybrid journals that published at least one open access article
between 2019 and 2023, based on open access status information from each
database. Only original research articles and reviews were considered in
the analysis.

\begin{figure}[ht!]

\includegraphics[width=0.99\linewidth,height=\textheight,keepaspectratio]{fig/fig-upset_coverage_results-1.png}

\caption{\label{fig-upset_coverage_results}Upset graph}

\end{figure}%

Journal coverage analysis revealed that 66\% (n = 7,970) of hybrid
journals included in transformative agreements were indexed in all three
databases ( \ref{fig-upset_coverage_results}A). The second-largest set
consisted of journals indexed in both hoaddata and Scopus, comprising
21\% (n = 2,595) of hybrid journals. Notably, 6\% (n = 739) of journals
were exclusively contained in hoaadata, while 3\% (n = 354) were only
found in the proprietory databases Scopus and Web of Science. Upon
insepction, this latter group represents hybrid journals for which no
open access evidence could be retrieved from Crossref, which serves as
the open access evidence source for hoaddata.

In terms of article coverage, Fig B shows the DOI overlap,
distinguihsing between a shared corpus and just those where a DOI was
only available through hoaddata. Upon inspection, reasons for lackign
DOI coverage in proprietory database were different publication dates
and differenc ein document type definitions. As such, demosntrates
certain uncertainies using the open approach. Overall, The majority of
articles can be found

Using DOIs also the size of journals were calculated (Fig C). It
highlights thate large spread in the intersection between all three
datasett. Journals are, on average, smaller than those just covered by
one or two sources.In particular journals exlcusively covered by
hoaddata are significant smaller than those covered by all three
sources.

This study compares results drawn from the openly available and
regularly updated hoaddata, an R package leveraging the open scholarly
data sources Crossref and OpenAlex, with the in-house database of the
German Competence Network Overall, xxxx hybrid journals included in xxx
agreements that published at least one open access article between 2019
and 2023.

@@

\bibitem[\citeproctext]{ref-ComplexUpset}
Krassowski, M. (2020). \emph{ComplexUpset}.
\url{https://doi.org/10.5281/zenodo.3700590}

\bibitem[\citeproctext]{ref-Lex_2014}
Lex, A., Gehlenborg, N., Strobelt, H., Vuillemot, R., \& Pfister, H.
(2014). UpSet: Visualization of intersecting sets. \emph{IEEE
Transactions on Visualization and Computer Graphics}, \emph{20}(12),
1983--1992. \url{https://doi.org/10.1109/tvcg.2014.2346248}

@@

\bibitem[\citeproctext]{ref-Melero_Fuentes_2025}
Melero-Fuentes, D., Aguilar-Moya, R., Valderrama-Zurián, J.-C., \&
Gorraiz, J. (2025). Evolution and effect of meeting abstracts in JCR
journals. \emph{Journal of Informetrics}, \emph{19}(1), 101631.
\url{https://doi.org/10.1016/j.joi.2024.101631}
